---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
library(ISLR)
data(OJ)

summary(OJ)

```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
```{r}
set.seed(1234)
split <- sample(1:nrow(OJ),0.7*nrow(OJ))
train <- OJ[split,]
test <- OJ[-split,]

summary(train)
```
```{r}
mean(train$PriceMM)
mean(train$DiscMM)
#priceMinuteMaid <- train[OJ$]
week275 <- OJ[OJ$WeekofPurchase == 275, 'Purchase']
```
```{r}

tree1 <- rpart(Purchase~PriceCH+PriceMM+DiscCH+DiscMM+SpecialCH+SpecialMM+LoyalCH+PriceDiff+PctDiscMM+PctDiscCH,data = train, method = 'class')

pred <- predict(tree1, type='prob', newdata=test)[,2]
#pred2_test = predict(tree2, type='prob', newdata = test)[,2]
library(ROCR)
ROCRpred <- prediction(predictions = pred, labels = test$Purchase)
auc <- as.numeric(performance(prediction.obj = ROCRpred,measure = 'auc')@y.values); auc
```
```{r}
#tree2 <- rpart(Purchase~PriceCH+PriceMM+DiscCH+DiscMM+SpecialCH+SpecialMM+LoyalCH+PriceDiff+PctDiscMM+PctDiscCH,data = train, method = 'class', control = rpart.control(minsplit = 10, cp = 0.001))

library(caret)
library(lattice)
trControl <- trainControl(method='cv',number = 10)
tuneGrid <- expand.grid(.cp = seq(from = 0,to = 0.1,by = 0.001))
set.seed(100)
cvModel <- train(Purchase~PriceCH+PriceMM+DiscCH+DiscMM+SpecialCH+SpecialMM+LoyalCH+PriceDiff+PctDiscMM+PctDiscCH,
                data=train,
                method="rpart",
                trControl = trControl,
                tuneGrid = tuneGrid)

cvModel$results

library(ggplot2)
ggplot(data=cvModel$results, aes(x=cp, y=Accuracy))+
  geom_line(size=0.5,alpha=0.2)+
  geom_point(color='brown')+
  theme_bw()+
  ggtitle(label=paste('Highest Accuract is at a cp of ',cvModel$bestTune$cp))
```
```{r}
tree2 <- rpart(Purchase~PriceCH+PriceMM+DiscCH+DiscMM+SpecialCH+SpecialMM+LoyalCH+PriceDiff+PctDiscMM+PctDiscCH,data = train, method = 'class', control = rpart.control(cp = 0.006))

pred2 <- predict(tree2,newdata=test, type='prob')
ROCRpred2 <- prediction(pred2[,2],test$Purchase)
auc2 <- as.numeric(performance(prediction.obj = ROCRpred2,measure = 'auc')@y.values); auc2

```
```{r}
library(ipred)
set.seed(617)
bag <- bagging(Purchase~PriceCH+PriceMM+DiscCH+DiscMM+SpecialCH+SpecialMM+LoyalCH+PriceDiff+PctDiscMM+PctDiscCH,
              data = train,
              nbagg = 1000)

#pred_train <- predict(bag, type = "prob")
pred3 <- predict(bag, newdata=test, type='prob')
ROCRpred3 <- prediction(pred3[,2],test$Purchase)
auc3 <- as.numeric(performance(prediction.obj = ROCRpred3,measure = 'auc')@y.values); auc3
```
```{r}
library(randomForest)
set.seed(617)
forest <- randomForest(Purchase~PriceCH+PriceMM+DiscCH+DiscMM+SpecialCH+SpecialMM+LoyalCH+PriceDiff+PctDiscMM+PctDiscCH,
                      train,
                      ntree = 1000)

pred4 <- predict(forest, newdata=test, type='prob')
ROCRpred4 <- prediction(pred4[,2],test$Purchase)
auc4 <- as.numeric(performance(prediction.obj = ROCRpred4,measure = 'auc')@y.values); auc4

```
```{r}
train$Purchase2 <- as.numeric(train$Purchase)-1
test$Purchase2 <- as.numeric(test$Purchase)-1

library(gbm)
set.seed(617)
boost <- gbm(Purchase2~PriceCH+PriceMM+DiscCH+DiscMM+SpecialCH+SpecialMM+LoyalCH+PriceDiff+PctDiscMM+PctDiscCH,
            data=train,
            distribution="bernoulli",
            n.trees = 1000,
            interaction.depth = 1,
            shrinkage = 0.04)
pred5 <- predict(boost, newdata = test, type = "response", n.trees = 100)
ROCRpred5 <- prediction(pred5,test$Purchase2)
auc5 <- as.numeric(performance(prediction.obj = ROCRpred5,measure = 'auc')@y.values); auc5

```
