---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
setwd('/Users/emilyziyixiao/DataspellProjects/Framework&MethodsHW/')

wages <- read.csv('assignment7_wages.csv',stringsAsFactors = TRUE)
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
```{r}
wages <- wages[wages$earn>0,]

summary(wages)
```
```{r}
black_earn <- wages[wages$race == 'black', "earn"]
white_earn <- wages[wages$race == 'white', "earn"]
hispanic_earn <- wages[wages$race == 'hispanic', "earn"]
other_earn <- wages[wages$race == 'other', "earn"]

mean(black_earn)
mean(white_earn)
mean(hispanic_earn)
mean(other_earn)
```
```{r}
set.seed(1731)
split <- sample(1:nrow(wages),0.75*nrow(wages))
train <- wages[split,]
test <- wages[-split,]

mean(train$earn)
mean(train$height)
```
```{r}
model1 <- lm(earn~height+sex+race+ed+age,data=train)
summary(model1)
pred <- predict(model1)
rmse1 <- sqrt(mean((pred-train$earn)^2)); rmse1
```
```{r}
library(ggplot2)
ggplot(data=train,aes(y=earn,x=ed))+
  geom_bar(stat="summary",fun="mean",fill='cadetblue')+
  facet_wrap(~sex)+
  theme_bw()

ggplot(data=train,aes(y=earn,x=ed,color=sex))+
  geom_smooth(method="lm",se=F,size=1.2)+
  scale_x_continuous(breaks=c(seq(2,20,2)))+
  scale_y_continuous(breaks=c(seq(0,100000,10000)))+
  theme_bw()

```
```{r}
model_sex_ed <- lm(earn~sex + ed + sex*ed,data=train)
summary(model_sex_ed)
```
```{r}
model2 <- lm(earn~height+sex+race+ed+age+sex*ed,data=train)
summary(model2)
pred <- predict(model2)
rmse2 <- sqrt(mean((pred-train$earn)^2)); rmse2

```
```{r}
model3 <- lm(earn~height+sex+race+ed+age+sex*ed+sex*age,data=train)
summary(model3)
pred <- predict(model3)
rmse3 <- sqrt(mean((pred-train$earn)^2)); rmse3
```
```{r}
model4 <- lm(earn~height+sex+race+ed+age+sex*ed+sex*age+age*ed,data=train)
summary(model4)
pred <- predict(model4)
rmse4 <- sqrt(mean((pred-train$earn)^2)); rmse4
```
```{r}
model5 <- lm(earn~(height+sex+race+ed+age)^2,data=train)
summary(model5)
pred <- predict(model5)
rmse5 <- sqrt(mean((pred-train$earn)^2)); rmse5
```
```{r}
pred5_test <- predict(model5, newdata = test)
rmse5_test <- sqrt(mean((pred5_test - test$earn)^2)); rmse5_test
```
```{r}
library(rpart)
library(rpart.plot)

tree1 <- rpart(earn~height+sex+race+ed+age,data = train)
#rpart.plot(tree1, digits=5)
prp(tree1,digits=5)

pred <- predict(tree1)
rmse6 <- sqrt(mean((pred-train$earn)^2)); rmse6

```
```{r}
pred6_test <- predict(tree1, newdata = test)
rmse6_test <- sqrt(mean((pred6_test - test$earn)^2)); rmse6_test
```
```{r}
treeSimp1 <- rpart(earn~.,data=train,control=rpart.control(minbucket=20))
prp(treeSimp1,digits=5)

pred <- predict(treeSimp1)
rmse7 <- sqrt(mean((pred-train$earn)^2)); rmse7
```
```{r}
treeSimp2 <- rpart(earn~.,data=train,control=rpart.control(minbucket=50))
prp(treeSimp2,digits=5)

pred <- predict(treeSimp2)
rmse8 <- sqrt(mean((pred-train$earn)^2)); rmse8
```
```{r}
pred8_test <- predict(treeSimp2, newdata = test)
rmse8_test <- sqrt(mean((pred8_test - test$earn)^2)); rmse8_test

```
```{r}
treeComplex1 <- rpart(earn~.,data=train,control=rpart.control(minbucket=5))
prp(treeComplex1,digits=5)

pred <- predict(treeComplex1)
rmse9 <- sqrt(mean((pred-train$earn)^2)); rmse9
```
```{r}
treeComplex2 <- rpart(earn~.,data=train,control=rpart.control(minbucket=1))
prp(treeComplex2,digits=5)

pred <- predict(treeComplex2)
rmse10 <- sqrt(mean((pred-train$earn)^2)); rmse10
```
```{r}
pred10_test <- predict(treeComplex2, newdata = test)
rmse10_test <- sqrt(mean((pred10_test - test$earn)^2)); rmse10_test
```
```{r}
trControl = trainControl(method='cv',number = 5)
tuneGrid = expand.grid(.cp = seq(from = 0.001,to = 0.1,by = 0.001))
set.seed(617)
cvModel = train(earn~.,
                data=train,
                method="rpart",
                trControl = trControl,
                tuneGrid = tuneGrid)

cvModel$results

library(ggplot2)
ggplot(data=cvModel$results, aes(x=cp, y=RMSE))+
  geom_line(size=0.5,alpha=0.2)+
  geom_point(color='brown')+
  theme_bw()+
  ggtitle(label=paste('Lowest RMSE is at a cp of ',cvModel$bestTune$cp))
```
